Transfer report

### 2018-08-10 Report/paper-data.Rmd
Adds arne's report

```{r setup, include=FALSE}
library(ggplot2)
library(ez)
library(dplyr)
library(reshape2)
library(broom)
library(brainvr.R)
library(restimoter)

@@

conference_walk_all <- walk_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
conference_sop_all <- sop_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
load("../multi.data")

@@

#Number of participants
```{r}
walk_all %>% group_by(condition) %>% summarise(N = n_distinct(id))
```

# Visualisations

# Walking visualisations
VR

```{r, echo=F}
plot_walk_trial(ls$tw67$phase1, 1)
```

REal world
```{r, echo=F}
plot_walk_trial(ls$tw64$phase2, 17)
```

# Pointing visualisations
VR
```{r, echo=F}
plot_all(ls$tw64$phase1, 1:6, plot_sop_point)
plot_sop_point(ls$tw64$phase1, 3)
```

Real wolrd
```{r, echo=F}
plot_all(ls$tw64$phase2, 1:6, plot_sop_point)
plot_sop_point(ls$tw64$phase2, 3)
```

@@

ggplot(conference_walk_all, aes(x = exp_block_id, y = min_norm_distance, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 3, linetype=4) +
  ylab("Average normalised trial distance") + xlab("Block") + 
  scale_color_manual(values=estimote_pal,"Condition") + guides(fill=F)

ggplot(conference_walk_all, aes(x = exp_trial_id, y = min_norm_distance, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 18, linetype=4) +
  ylab("Average normalised trial distance") + xlab("Block number") + 
  scale_color_manual(values=estimote_pal, "Condition")

ggplot(conference_walk_all, aes(x = exp_block_id, y = errors, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 3, linetype=4) +
  ylab("Number of mistakes in office decision") + xlab("Block number") + 
  scale_color_manual(values=estimote_pal, "Condition")

@@

## Average pointing in all conditions
```{r, echo=F, warnings = F}
ggplot(sop_all[sop_all$phase == 1, ], aes(x = condition, y = abs(error), fill=factor(condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average pointing error in degrees in the first phase") + xlab("Condition") + 
  scale_fill_manual(values = estimote_pal, "Phase")

ggplot(sop_all[sop_all$phase == 2, ], aes(x = condition, y = abs(error), fill=factor(condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average pointing error in degrees in second phase") + xlab("Condition") + 
  scale_fill_manual(values = estimote_pal) + guides(fill=F)

ggplot(sop_all[sop_all$phase == 1, ], aes(x = learning.condition, y = abs(error), fill=factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average pointing error in degrees in the first phase") + xlab("Condition") + 
  scale_fill_manual(values = estimote_pal) + guides(fill=F)

ggplot(sop_all[sop_all$phase == 2, ], aes(x = testing.condition, y = abs(error), fill=factor(testing.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average pointing error in degrees in second phase") + xlab("Condition") + 
  scale_fill_manual(values = estimote_pal) + guides(fill=F)

#t.test(abs(error) ~ learning.condition, sop_all[sop_all$phase == 1,])
t.test(abs(error) ~ testing.condition, sop_all[sop_all$phase == 2,])
```

@@

## Sum of errors
Measure of overall sum of errors. Mean columns define mean sum of errors for all participants in that block
```{r, echo=F, warnings = F}
df <- block_measure(condition_all_sums, "sum.errors")
df
ggplot(melt(df[,1:4]), aes(x = learning.condition, y = value, fill = variable)) + 
  geom_bar(stat = 'identity', position="dodge") + 
  scale_fill_manual(values = estimote_pal) +
  ylab("Mean sum of errors") + xlab("Learning condition")  + guides(fill=F)

@@

Measure of mean distance. First three columns define mean normalised distance in each block.
```{r, echo=F, warnings = F}
df <- block_measure(condition_all_sums, "mean.distance")
df
ggplot(melt(df[,1:4]), aes(x = learning.condition, y = value, fill = variable)) + 
  scale_fill_manual(values = estimote_pal) +
  geom_bar(stat = 'identity', position="dodge") + ylab("Mean normalised distance")

@@

### Block 3-4
Paired t tests between min normalised distance difference in blocks 3 and 4.
```{r, echo=F}
block_t_test(conference_walk_all, 4, 3,"min_norm_distance")
```

And for number of errors
```{r, echo=F}
block_t_test(conference_walk_all, 4, 3,"errors")
```

### Block 1-4
Paired t tests between min normalised distance difference in blocks 1 and 4.
```{r, echo=F}
block_t_test(conference_walk_all, 4, 1,"min_norm_distance")
```
And for number of errors
```{r, echo=F}
block_t_test(conference_walk_all, 4, 1,"errors")
```

### Block 1-6
Paired t tests between min normalised distance difference in blocks 1 and 6.
```{r, echo=F}
block_t_test(conference_walk_all, 6, 1,"min_norm_distance")
```
And for number of errors
```{r, echo=F}
block_t_test(conference_walk_all, 6, 1,"errors")
```

## Independent block improvement comparisons between conditions for distance

@@

### Block 1-4 improvement
VE-real and real-real
```{r, echo=F}
t.test(df_wide$diff41[df_wide$learning.condition=="Desktop"],df_wide$diff41[df_wide$learning.condition=="Real"])
```

VR-real and real-real
```{r, echo=F}
t.test(df_wide$diff41[df_wide$learning.condition=="Treadmill VR"],df_wide$diff41[df_wide$learning.condition=="Real"])  
```

VR-real and VE-real
```{r, echo=F}
t.test(df_wide$diff41[df_wide$learning.condition=="Treadmill VR"],df_wide$diff41[df_wide$learning.condition=="Desktop"])
```

### Block 3-4 improvement
Desktop to real
```{r, echo=F}
t.test(df_wide$diff43[df_wide$learning.condition=="Desktop"], df_wide$diff43[df_wide$learning.condition=="Real"])
```

VR-real and real-real
```{r, echo=F}
t.test(df_wide$diff43[df_wide$learning.condition=="Treadmill VR"], df_wide$diff43[df_wide$learning.condition=="Real"])  
```

VR-real and VE-real
```{r, echo=F}
t.test(df_wide$diff43[df_wide$learning.condition=="Treadmill VR"], df_wide$diff43[df_wide$learning.condition=="Desktop"])
```

@@

### Block 1-4 improvement
VE-real and real-real
```{r, echo=F}
t.test(df_wide$diff41[df_wide$learning.condition=="Desktop"],df_wide$diff41[df_wide$learning.condition=="Real"])
```

VR-real and real-real
```{r, echo=F}
t.test(df_wide$diff41[df_wide$learning.condition=="Treadmill VR"],df_wide$diff41[df_wide$learning.condition=="Real"])  
```

VR-real and VE-real
```{r, echo=F}
t.test(df_wide$diff41[df_wide$learning.condition=="Treadmill VR"],df_wide$diff41[df_wide$learning.condition=="Desktop"])
```

### Block 3-4 improvement
Desktop to real
```{r, echo=F}
t.test(df_wide$diff43[df_wide$learning.condition=="Desktop"], df_wide$diff43[df_wide$learning.condition=="Real"])
```

VR-real and real-real
```{r, echo=F}
t.test(df_wide$diff43[df_wide$learning.condition=="Treadmill VR"], df_wide$diff43[df_wide$learning.condition=="Real"])  
```

VR-real and VE-real
```{r, echo=F}
t.test(df_wide$diff43[df_wide$learning.condition=="Treadmill VR"], df_wide$diff43[df_wide$learning.condition=="Desktop"])
```

## Anova
Simple between subjects anova
```{r, echo=F}
aov_block_distance <- aov(min_norm_distance~exp_block_id*learning.condition, conference_walk_all)
summary(aov_block_distance)
```

@@

```{r, warning = F, echo=F, message=F}
aov_block_dist_34 <- ezANOVA(
  data = clean_walk_34,
  dv = min_norm_distance, 
  wid = id,
  within = exp_block_id,
  between = learning.condition, 
  type = 3)
aov_block_dist_34

@@

```{r, warning = F, echo=F, message=F}
aov_block_dist_14 <- ezANOVA(
  data = clean_walk_14,
  dv = min_norm_distance, 
  wid = id,
  within = exp_block_id,
  between = learning.condition,
  type = 3)
aov_block_dist_14

@@

### NUmber of errors
Within subjects anova for block 1-4 number of errors.

```{r, warning = F, echo=F, message=F}
aov_block_err_14 <- ezANOVA(
  data = clean_walk_14,
  dv = errors, 
  wid = id,
  within = exp_block_id,
  between = learning.condition,
  type = 3)
aov_block_err_14

@@

Within subjects anova for block 3-4 number of errors.
```{r, warning = F, echo=F, message=F}
aov_block_err_34 <- ezANOVA(
  data = clean_walk_34,
  dv = errors, 
  wid = id,
  within = exp_block_id,
  between = condition,
  type = 3)
aov_block_err_34

>>>>

```{r setup, include=FALSE}
library(ggplot2)
library(ez)
library(Hmisc)
library(knitr)
library(dplyr)
library(reshape2)
library(broom)
library(brainvr.R)
library(xtable)
library(restimoter)

@@

conference_walk_all <- walk_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
conference_sop_all <- sop_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))

@@

@@

ggplot(conference_walk_all, aes(x = exp_block_id, y = min_norm_distance, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 3.5, linetype=4) +
  ylab("Average normalised trial distance") + xlab("Block") + 
  scale_color_manual(values=estimote_pal,"Condition") + guides(fill=F)

ggplot(conference_walk_all, aes(x = exp_trial_id, y = min_norm_distance, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 18.5, linetype=4) +
  ylab("Average normalised trial distance") + xlab("Block number") + 
  scale_color_manual(values=estimote_pal, "Condition")

ggplot(conference_walk_all, aes(x = exp_block_id, y = errors, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 3.5, linetype=4) +
  ylab("Number of mistakes in office decision") + xlab("Block number") + 
  scale_color_manual(values=estimote_pal, "Condition")

@@

@@

## Sum of errors
Measure of overall sum of errors. Mean columns define mean sum of errors for all participants in that block
```{r, echo=F, warnings = F}
df <- block_measure(condition_all_sums, "sum.errors")
kable(df)
ggplot(melt(df[,1:4]), aes(x = learning.condition, y = value, fill = variable)) + 
  geom_bar(stat = 'identity', position="dodge") + 
  scale_fill_manual(values = estimote_pal) +
  ylab("Mean sum of errors") + xlab("Learning condition")  + guides(fill=F)

@@

Measure of mean distance. First three columns define mean normalised distance in each block.
```{r, echo=F, warnings = F}
df <- block_measure(condition_all_sums, "mean.distance")
kable(df)
ggplot(melt(df[,1:4]), aes(x = learning.condition, y = value, fill = variable)) + 
  scale_fill_manual(values = estimote_pal) +
  geom_bar(stat = 'identity', position="dodge") + ylab("Mean normalised distance")

@@

### Block 3-4
Paired t tests between min normalised distance difference in blocks 3 and 4.
```{r, echo=F}
kable(block_t_test(conference_walk_all, 4, 3,"min_norm_distance"))
```

And for number of errors
```{r, echo=F}
kable(block_t_test(conference_walk_all, 4, 3,"errors"))
```

### Block 1-4
Paired t tests between min normalised distance difference in blocks 1 and 4.
```{r, echo=F}
kable(block_t_test(conference_walk_all, 4, 1,"min_norm_distance"))
```
And for number of errors
```{r, echo=F}
kable(block_t_test(conference_walk_all, 4, 1,"errors"))
```

### Block 1-6
Paired t tests between min normalised distance difference in blocks 1 and 6.

```{r, echo=F}
kable(block_t_test(conference_walk_all, 6, 1,"min_norm_distance"))
```

And for number of errors

```{r, echo=F}
kable(block_t_test(conference_walk_all, 6, 1,"errors"))
```

## Independent block improvement comparisons between conditions for distance
```{r, echo=F}
report_independent_comparisons <- function(df_wide, column){
  desktop_real <- t.test(df_wide[df_wide$learning.condition=="Desktop", column],df_wide[df_wide$learning.condition=="Real", column])
  treadmill_real <- t.test(df_wide[df_wide$learning.condition=="Treadmill VR", column],df_wide[df_wide$learning.condition=="Real", column])  
  treadmill_desktop <- t.test(df_wide[df_wide$learning.condition=="Treadmill VR", column],df_wide[df_wide$learning.condition=="Desktop", column])
  results <- list(desktop_real, treadmill_real, treadmill_desktop)
  df <- data.frame(`Comparison`=c("Desktop - real", "Treadmil - real", "Treadmil- Desktop"), mean.first=sapply(results, function(x){x$estimate[1]}), mean.second=sapply(results, function(x){x$estimate[2]}), `p-value`=sapply(results, function(x){x$p.value}))
  return(df)
}
```

@@

### Block 1-4 improvement
```{r, echo=F}
kable(report_independent_comparisons(df_wide, "diff41"))
```

### Block 3-4 improvement
```{r, echo=F}
kable(report_independent_comparisons(df_wide, "diff43"))
```

@@

### Block 1-4 improvement
```{r, echo=F}
kable(report_independent_comparisons(df_wide, "diff41"))
```

### Block 3-4 improvement
```{r, echo=F}
kable(report_independent_comparisons(df_wide, "diff43"))
```

## Anova
Simple between subjects anova
```{r, echo=F}
aov_block_distance <- aov(min_norm_distance~exp_block_id*learning.condition, conference_walk_all)
kable(anova_table(aov_block_distance))
```

@@

```{r, warning = F, echo=F, message=F}
aov_block_dist_34 <- ezANOVA(
  data = clean_walk_34,
  dv = min_norm_distance, 
  wid = id,
  within = exp_block_id,
  between = learning.condition, 
  type = 3)
kable(aov_block_dist_34)

@@

```{r, warning = F, echo=F, message=F}
aov_block_dist_14 <- ezANOVA(
  data = clean_walk_14,
  dv = min_norm_distance, 
  wid = id,
  within = exp_block_id,
  between = learning.condition,
  type = 3)
kable(aov_block_dist_14)

@@

### Number of errors
Within subjects anova for block 1-4 number of errors.

```{r, warning = F, echo=F, message=F}
aov_block_err_14 <- ezANOVA(
  data = clean_walk_14,
  dv = errors, 
  wid = id,
  within = exp_block_id,
  between = learning.condition,
  type = 3)
kable(aov_block_err_14)

@@

Within subjects anova for block 3-4 number of errors.
```{r, warning = F, echo=F, message=F}
aov_block_err_34 <- ezANOVA(
  data = clean_walk_34,
  dv = errors, 
  wid = id,
  within = exp_block_id,
  between = condition,
  type = 3)
kable(aov_block_err_34)
